---
output:
  github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "examples/README-"
)

library(tadaatoolbox)

description <- as.data.frame(read.dcf("DESCRIPTION"), stringsAsFactors = F)
```

# tadaatoolbox   

[![Build Status](https://travis-ci.org/tadaadata/tadaatoolbox.svg)](https://travis-ci.org/tadaadata/tadaatoolbox)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/tadaatoolbox)](http://cran.r-project.org/package=tadaatoolbox)
[![CRAN_Downloads_Badge](http://cranlogs.r-pkg.org/badges/grand-total/tadaatoolbox)](http://cran.r-project.org/package=tadaatoolbox)
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)

This is **tadaatoolbox** version ``r description$Version`` ([semver](http://semver.org/)).<br />
It contains helpers for data analysis and presentation focused on undergrad psychology, the target audience being students at University of Bremen. 

Please consider this as a teaching project and be careful if you intend to use it for production use.<br />
To see what's new, see [NEWS.md](https://github.com/tadaadata/tadaatoolbox/blob/master/NEWS.md).

As a sideproject, I attempted to visualize the package depencencies [in this document](http://htmlpreview.github.io/?https://github.com/tadaadata/tadaatoolbox/blob/master/dev/dependencies/dependencies.html). It's not optimal yet, but at least it's a glimpse of the first two layers of dependencies.

# Installation

Install the current development version from GitHub (recommended):

```
if (!("devtools" %in% installed.packages())){
  install.packages("devtools")
}

devtools::install_github("tadaadata/tadaatoolbox")
```

Or install the most recent stable version from CRAN:

```
install.packages("tadaatoolbox")
```

# Contribution

Please do! I have no idea where I'm going with this. Feel free to [open issues](https://github.com/tadaadata/tadaatoolbox/issues).

## Contributers

```{r contrib, echo = F}
contrib <- eval(parse(text = description$`Authors@R`))

names <- sapply(contrib, function(x){
              paste(x[[1]]$given, x[[1]]$family)
            }) 
roles <- sapply(contrib, function(x){
              paste(x[[1]]$role, collapse = " & ")
            }) 

knitr::kable(data.frame(Contributer = names, Role = roles))
```


# Functionality

See the included vignette for a demonstration: `browseVignettes("tadaatoolbox")` or view the current 
version in this repository [via GitHubs HTML preview](http://htmlpreview.github.io/?https://github.com/tadaadata/tadaatoolbox/blob/master/vignettes/overview.html).

## Statistical functions

* `modus`: A simple function to extract the mode of a frequency table
* `nom_chisqu`: Simple wrapper for `chisq.test` that produces a single value.
* `nom_phi`: Simple wrapper for `vcd::assocstats` to extract phi.
* `nom_v`: Simple wrapper for `vcd::assocstats` to extract Cramer's V.
* `nom_c`: Simple wrapper for `vcd::assocstats` to extract the contingency coefficient c.
* `nom_lambda`: Simple wrapper for `ryouready::nom.lambda` to extract appropriate lambda.
* `ord_gamma`: Simple wrapper for `ryouready::ord.gamma`.
* `ord_somers_d`: Simple wrapper for `ryouready::ord.somers.d`.

### Summaries

* `tadaa_nom`: All the nominal stats in one table.
* `tadaa_ord`: All the ordinal stats in one table.

## Misc. helpers

* `generate_recodes`: To produce recode assignments for `car::recode` for evenly sequenced clusters.
* `interval_labels`: To produce labels for clusters created by `cut`.

## Tidy test output

* `tadaa_aov`: For `aov` with included partial eta^2.
* `tadaa_t.test`: For `t.test` with automatic homogenity of variance detection, effect size and power.

## Helpers for plots

### CI based on t-distribution

* `mean_ci_t`: Returns a `data.frame` with `y` (`mean`), `ymin` and `ymax` for the CI bounds.
    * `confint_t`: For the underlying function to get the CI width. Returns a single value.

### Interaction plots

* `tadaa_int`: Simple interaction plot template.
