---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "examples/README-"
)
```

# tadaatoolbox   

[![Build Status](https://travis-ci.org/tadaadata/tadaatoolbox.svg)](https://travis-ci.org/tadaadata/tadaatoolbox)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/tadaatoolbox)](http://cran.r-project.org/package=tadaatoolbox)
[![Project Status: Wip - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/0.1.0/wip.svg)](http://www.repostatus.org/#wip)

This is a mere toolbox of common convenience function meant to ease workflows.

# Installation

```
if (!("devtools" %in% installed.packages())){
  install.packages("devtools")
}

devtools::install_github("tadaadata/tadaatoolbox")
```

# Examples

## Statistical functions

* `modus`: A simple function to extract the mode of a frequency table
* `nom_chisqu`: Simple wrapper for `chisq.test` that produces a single value.
* `nom_phi`: Simple wrapper for `vcd::assocstats` to extract phi.
* `nom_v`: Simple wrapper for `vcd::assocstats` to extract Cramer's V.
* `nom_c`: Simple wrapper for `vcd::assocstats` to extract the contingency coefficient c.
* `nom_lambda`: Simple wrapper for `ryouready::nom.lambda` to extract appropriate lambda.
* `ord_gamma`: Simple wrapper for `ryouready::ord.gamma`.
* `ord_somers_d`: Simple wrapper for `ryouready::ord.somers.d`.

## Misc. helpers

* `generate_recodes`: To produce recode assignments for `car::recode` for evenly sequenced clusters.
* `interval_labels`: To produce labels for clusters created by `cut`.

## Tidy test output

### t-Tests

```{r t-test}
library(tadaatoolbox)
library(loldata)

tadaa_t.test(penis, length_flaccid, Method, print = "markdown")
```

### ANOVA

```{r anova}
library(tadaatoolbox)
library(loldata)

tadaa_aov(length_flaccid ~ Region, data = penis, print = "markdown")
```

## Helpers for plots

### CI based on t-distribution: `mean_ci_t` and `confint_t`

```{r confint}
library(ggplot2)
library(tadaatoolbox)
library(loldata)

ggplot(data = penis, aes(x = Region, y = length_flaccid)) +
  stat_summary(fun.data = "mean_ci_t", geom = "errorbar")
```

### Interaction plots

```{r interaction_plots}
tadaa_int(data = qmtut::ngo, response = stunzahl, group1 = jahrgang, group2 = geschl)
```

