---
output:
  github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "examples/README-"
)

description <- as.data.frame(read.dcf(system.file("DESCRIPTION", package = "tadaatoolbox")), stringsAsFactors = F)
```

# tadaatoolbox   

[![Build Status](https://travis-ci.org/tadaadata/tadaatoolbox.svg)](https://travis-ci.org/tadaadata/tadaatoolbox)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version-ago/tadaatoolbox)](https://cran.r-project.org/package=tadaatoolbox)
[![CRAN_Downloads_Badge](https://cranlogs.r-pkg.org/badges/tadaatoolbox)](https://cran.r-project.org/package=tadaatoolbox)
[![Coverage status](https://codecov.io/gh/tadaadata/tadaatoolbox/branch/master/graph/badge.svg)](https://codecov.io/github/tadaadata/tadaatoolbox?branch=master)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.1494965.svg)](https://doi.org/10.5281/zenodo.1494965)


`tadaatoolbox` contains helpers for data analysis and presentation focused on undergrad psychology, the target audience being students at University of Bremen. 

Please consider this as a teaching project and be careful if you intend to use it for production use.<br />
To see what's new, see [NEWS.md](https://github.com/tadaadata/tadaatoolbox/blob/master/NEWS.md).  
Also, since this project is still in the `0.x.y` version, you should expect the API to change at any time. Once we reach `1.0.0`, API changes will be rolled out more slowly and include deprecation warnings. In the meantime, the package is available on CRAN primarily for convenience, because its target audience is likely not familiar with GitHub or `devtools`.

# Installation

Install the current development version from GitHub (recommended):

```r
if (!("remotes" %in% installed.packages())){
  install.packages("remotes")
}

remotes::install_github("tadaadata/tadaatoolbox")
```

Or install the most recent stable version from CRAN:

```r
install.packages("tadaatoolbox")
```

# Contribution

Please do! I have no idea where I'm going with this. Feel free to [open issues](https://github.com/tadaadata/tadaatoolbox/issues).

## Contributers

```{r contrib, echo = F}
contrib <- eval(parse(text = description$`Authors@R`))

names <- sapply(contrib, function(x){
              paste(x[[1]]$given, x[[1]]$family)
            }) 
roles <- sapply(contrib, function(x){
              roles <- paste(x[[1]]$role, collapse = " & ")
              roles <- sub("aut", "Author", roles)
              roles <- sub("ctb", "Contributor", roles)
              roles <- sub("cre", "Maintainer", roles)
              return(roles)
            }) 

knitr::kable(data.frame(Contributer = names, Role = roles))
```

# Functionality

See the included vignette for a demonstration: `browseVignettes("tadaatoolbox")` or view [the `pkgdown`ed version of this repo](https://tadaatoolbox.tadaa-data.de) for an overview and function index.  
Here's a few highlights:

## Tidy (as in pretty) test output

See all of them in action [in this vignette](https://tadaatoolbox.tadaa-data.de/articles/test_output.html)

* `tadaa_aov`: For 3 flavours of `aov` with included partial $\eta^2$, Cohen's f and power.
* `tadaa_kruskal`: A wrapper for `kruskal.test` tidied and optionally `pixiedust`ed.
* `tadaa_t.test`: For `t.test` with automatic homogenity of variance detection, effect size and power.
* `tadaa_wilcoxon`: A wrapper for `wilcox.test` tidied and optionally `pixiedust`ed.
* `tadaa_levene`: Wrapper for `car::leveneTest` tidied and optionally `pixiedust`ed.
* `tadaa_normtest` lets you do tests for normality (4 methods) over multiple variables.
* `tadaa_pairwise_t`, `tadaa_pairwise_gh` and `tadaa_pairwise_tukey` for various pairwise procedures.

## Helpers for plots

* `tadaa_int`: Simple interaction plot template.
* `tadaa_balance`: Check equality of group sizes.
* `tadaa_mean_ci`: Plots means with 95% confidence intervals as errorbars.
* `tadaa_plot_tukey`: For pretty `TukeyHSD` visualization.

# Dependencies

I rely on these awesome package for all the things this package does, so you might want to consider checking them out.

```{r deps, results='asis', echo=FALSE}
# I wodered how ugly I could make this. The answer is obvious.
cat(
  paste0("- **", 
           gsub(x = sub(x = gsub(x = strsplit(description$Imports, 
                                              ",\n")[[1]], 
                                 "\n", 
                                 ""), 
                        "stats, methods, ", 
                        ""), 
                ", ", 
                "**\n- **"), 
           "**", 
           collapse = "\n")
    )
```

# Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
